\subsection{Monitoring offshore wind turbines}

This group chose to explore the effects of digitalisation on forecasting for energy trading on 5- to 10-minute time scales.

They identified three actors involved in this at present:

\begin{itemize}
\item
  Alice, a wind farm operator. They currently record SCADA data and have no way to use this in their market. They are sometimes required to down-regulate their turbines by the grid operator.
\item
  Bob, a weather forecaster. They obtain satellite and other data to create a weather forecast
\item
  Chris, an energy trader. They trade energy from various sources.
\end{itemize}

Currently the three actors operate independently (Table \ref{tab:02_offshoreforecasting_now}). The group imagined a future state where the actors are able to interact and share data, enabling energy trading (Figure \ref{fig:02_offshoreforecasting_future}).

The group identified several things that would be needed to make this vision a reality:

\begin{enumerate}
\item
  \textbf{Good wind speed measurements from lidar}. The Lidar system
  with high range resolution would also need to provide a data flow to
  the forecaster. This should be provided by Lidar OEMs.
\item
  \textbf{Feedback from the market}. This would take the form of e.g., a
  command for regulation of the turbines. It was thought this would be
  provided by new companies.
\item
  \textbf{Improved forecasting method using lidar data}. Good forecasts
  are achieved with lidar data, so the data flow needs to be established
  between the wind farm operator and forecaster. This needs to be
  enabled by the forecasting company.
\item
  \textbf{Realtime data for energy trading and market flexibility} to enable real time energy trading. This needs to be done by Bob and the market.
\item
  \textbf{Standardized data formats}. We need standards for all data flows. This should be done by expert groups from IEA and IEC.
\end{enumerate}

The main potential barriers were seen as market regulations and the difficulty of establishing reliable, timely data flows.

