\subsection{Wind plant control}

This group chose to explore the concept of ``Smart wind farms:
Nacelle-mounted lidar for wind farm optimisation''. This is currently an area of active research but very limited commercial adoption (Table \ref{tab:03_windPlantControl_now}).

The future user story was split into two phases (Table \ref{tab:03_windPlantControl_future}). The first phase takes place during the project execution:

\begin{enumerate}
\item
  Fred invests into a development project
\item
  Fred and Alice together provide communication network, database,
  processing power
\item
  Diane provides consultancy and advanced control algorithms
\item
  Bob connects lidar to the network and integrates lidar (reacts to
  commands)
\end{enumerate}

The second phase was after the project was complete:

\begin{enumerate}
\setcounter{enumi}{4}
\item
  All together publish their success stories
\item
  This will push others to do the same and can build up on the
  experience
\item
  Bob and Alice can improve their lidar / turbine to make them even
  smarter and can add more features.
\item
  Diane can develop better algorithms
\item
  Fred is happy and invests into more smart wind farms!
\end{enumerate}

Several things were identified as being required to make this vision a reality:

\begin{enumerate}
\item
  \textbf{Proof of concept}. First successful field testing needed. This
  could be done through a research project or JIP
\item
  \textbf{A common interface}. This would allow communication between
  lidars, turbines and the wind farm controller. This could be done by
  IEA Wind Task 32 + new wind farm flow control task
\item
  \textbf{Understanding of economic benefit}. How much is there to gain?
  How much are the investment/maintenance costs? This could be done by a
  research project, JIP, or in collaboration with IEA Wind Task 37.
\end{enumerate}

The main barriers to this happening were:

\begin{enumerate}
\item
  Data privacy / security issues
\item
  Unwillingness to share intellectual property
\item
  Lack of budget for development.
\end{enumerate}

The group felt that the priority for 2021 should be an economic model to convince the various players to step in.